---
title: "Stroop Box"
author: "Shafiq"
date: "24/02/2022"
output: html_document
---


```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
library(data.table)
library(patchwork)
library(forcats)
library(knitr)
library(lubridate)
library(dplyr)
library(tidyr)
library(stringr)
library(MASS)
library(gplots)
library(RColorBrewer)
library(rmarkdown)
library(skimr)
library(ggpubr)
```


# Reading pilot data and descriptive stats 
```{r Reading pilot file, echo = FALSE, warning = FALSE}
setwd("C:/NIHR_Bioresource/Orginal_Data/Gene_and_cognition_study/Emma_har/G&C_Main_Phase1_Pilot_new/results_20200825_Modified_SPIDs")

bc.p <- fread("results_bc_20200825_PIDRemoved_MOD.csv") #9390
```

# Reading Main Data
```{r Reading data, echo = FALSE, warning = FALSE}
setwd("C:/NIHR_Bioresource/Orginal_Data/Gene_and_cognition_study/Emma_har/G&C_Main_Phase1_Cognitive_Data/G&P Main phase cognitive data - Part 1_Updated_17.06.2022")

bc.m <- fread("results_bc_20211130_PIDRemoved.csv") #622,140 rows
```


# Removing duplicates from main phase data
```{r stevens code}
bc.m_nodups <- bc.m %>% 
  mutate(time_stamp2 = dmy_hms(time_stamp)) %>% 
  arrange(barcode, question, time_stamp2) %>% 
  mutate(exactDuplicate = duplicated(.)) %>%  
  mutate(diffDateTimeDuplicate = !exactDuplicate & {dplyr::select(., barcode, question) %>% duplicated()}) 


dup_tests_removed <- bc.m_nodups %>% 
  filter(exactDuplicate | diffDateTimeDuplicate) 

dup_tests_removed %>% 
  group_by(barcode, exactDuplicate, diffDateTimeDuplicate) %>% 
  count()

bc.m_nodups <- bc.m_nodups %>% 
  filter(!exactDuplicate & !diffDateTimeDuplicate) %>% 
  dplyr::select(colnames(bc.m))
```


# Merging data 
```{r, echo = FALSE, warning = FALSE}
bc <- full_join(bc.p,bc.m_nodups) 
```


# Device: Creating readable device varriable
```{r Deive use, echo = FALSE, warning = FALSE}
bc$device_name2 <- as.character(bc$device_name)
bc$device_name2[grep("Windows", bc$device_name2, ignore.case = TRUE)] <- "Windows 10"
bc$device_name2[grep("iphone", bc$device_name2, ignore.case = TRUE)] <- "iPhone"
bc$device_name2[grep("android", bc$device_name2, ignore.case = TRUE)] <- "Android"
bc$device_name2 <- as.factor(bc$device_name2)
```

# Clean response in milisecond varriable: Replace value <=0 with Minimim non-zero score from data
```{r }
bc <- bc[order(bc$response_ms),]
zero_below <-bc %>% filter(response_ms<=0) 
bc_zeros_barcode <- unique(zero_below$barcode)

zero_below$iscorrect <- as.factor(zero_below$iscorrect)

zero_below_pers <- bc %>% filter(barcode=="xxxxxxxx")
zero_below_pers <- separate(zero_below_pers, question, into = c("test", "Number"), sep = 3, remove = FALSE)
zero_below_pers <- zero_below_pers[order(zero_below_pers$Number),]

bc$response_ms <- replace(bc$response_ms,bc$response_ms<=0, NA)

# Replacing Zero response time with minimum response time, echo=TRUE}
bc <- bc %>% replace_na(list(response_ms=2))
```


```{r Agrregating Stroop Box Test Data}
bc$Response_type <- ifelse(bc$iscorrect==0, "In-correct", "Correct")
bc$Response_type <- as.factor(bc$Response_type)


bc <- separate(bc, question, into = c("test", "Number"), sep = 3, remove = FALSE)

bc$bc_tests <- reorder(bc$question, bc$response_ms)
bc$Response_type_reorder <- reorder(bc$Response_type, bc$response_ms)

#Is correct 
bc_iscorrect_sum <- aggregate(bc$iscorrect, by = list(bc$barcode), FUN = sum)
colnames(bc_iscorrect_sum) <- c("barcode", "bc_correct_sum")

ids <- bc_iscorrect_sum %>% filter(bc_correct_sum>30) #zero


#is correct length
bc_iscorrect_length <- aggregate(bc$iscorrect, by = list(bc$barcode), FUN = length)
colnames(bc_iscorrect_length) <- c("barcode", "bc_correct_length")


#Mean response time and device
bc_Mean_ms <- plyr::ddply(bc, "barcode", summarise, bcMean_mil_sec = mean(response_ms), device_name2 = unique(device_name2))

bc_reduced <- list(bc_iscorrect_sum,bc_Mean_ms,bc_iscorrect_length) %>%
    Reduce(function(dtf1,dtf2) full_join(dtf1,dtf2,by="barcode"), .)


# measuring proportion of correct answer
bc_reduced$bc_correct_prop <- bc_reduced$bc_correct_sum/bc_reduced$bc_correct_length

```

```{r Saving Merged file}
setwd("C:/Gene_cognition_shafiq/02_Cleaning_Cognitive_data/Aggregated_Clean_Cognitive_Data")
fwrite(bc_reduced, file = "Stroop_Box_Aggregated_Feb2022.txt", sep = "\t", col.names = TRUE, row.names = FALSE, quote=FALSE)
```


