---
title: "Stroop Ink"
author: "Shafiq"
date: "28/02/2022"
output: html_document
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
library(data.table)
library(patchwork)
library(forcats)
library(knitr)
library(lubridate)
library(dplyr)
library(tidyr)
library(stringr)
library(MASS)
library(gplots)
library(RColorBrewer)
library(rmarkdown)
library(skimr)
library(ggpubr)
```

# Reading pilot data and descriptive stats 
```{r Reading pilot file, echo = FALSE, warning = FALSE}
setwd("C:/NIHR_Bioresource/Orginal_Data/Gene_and_cognition_study/Emma_har/G&C_Main_Phase1_Pilot_new/results_20200825_Modified_SPIDs")

ic.p <- fread("results_ic_20200825_PIDRemoved_MOD.csv") 
```

# Reading Main Data
```{r Reading data, echo = FALSE, warning = FALSE}
setwd("C:/NIHR_Bioresource/Orginal_Data/Gene_and_cognition_study/Emma_har/G&C_Main_Phase1_Cognitive_Data/G&P Main phase cognitive data - Part 1_Updated_17.06.2022")

ic.m <- fread("results_ic_20211130_PIDRemoved.csv")
```


# Removing duplicates from main phase data
```{r stevens code}

ic.m_nodups <- ic.m %>% 
  mutate(time_stamp2 = dmy_hms(time_stamp)) %>% 
  arrange(barcode, question, time_stamp2) %>% 
  mutate(exactDuplicate = duplicated(.)) %>%  
  mutate(diffDateTimeDuplicate = !exactDuplicate & {dplyr::select(., barcode, question) %>% duplicated()}) 

dup_tests_removed <- ic.m_nodups %>% 
  filter(exactDuplicate | diffDateTimeDuplicate) 

dup_tests_removed %>% 
  group_by(barcode, exactDuplicate, diffDateTimeDuplicate) %>% 
  count()

ic.m_nodups <- ic.m_nodups %>% 
  filter(!exactDuplicate & !diffDateTimeDuplicate) %>% 
  dplyr::select(colnames(ic.m))
```


# Merging Data 
```{r, echo = FALSE, warning = FALSE}
ic <- full_join(ic.p,ic.m_nodups) 
```


# Device: Creating readable device varriable
```{r Deive use, echo = FALSE, warning = FALSE}
ic$device_name2 <- as.character(ic$device_name)
ic$device_name2[grep("Windows", ic$device_name2, ignore.case = TRUE)] <- "Windows 10"
ic$device_name2[grep("iphone", ic$device_name2, ignore.case = TRUE)] <- "iPhone"
ic$device_name2[grep("android",ic$device_name2, ignore.case = TRUE)] <- "Android"
ic$device_name2 <- as.factor(ic$device_name2)
```

# Clean response in milisecond varriable: Replace value <=0 with Minimim non-zero score from data
```{r }
ic <- ic[order(ic$response_ms),]
zero_below <-ic %>% filter(response_ms<=0)
ic_zeros_barcode <- unique(zero_below$barcode)

zero_below$iscorrect <- as.factor(zero_below$iscorrect)

ic$response_ms <- replace(ic$response_ms,ic$response_ms<=0, NA)
ic <- ic %>% replace_na(list(response_ms=4))
```


```{r Aggregate Stroop Ink}
#is_correct_sum
ic_iscorrect_sum <- aggregate(ic$iscorrect, by=list(ic$barcode), FUN = sum)
colnames(ic_iscorrect_sum) <- c("barcode", "ic_correct_sum")


#is_correct_length
ic_iscorrect_length <- aggregate(ic$iscorrect, by=list(ic$barcode), FUN = length)
colnames(ic_iscorrect_length) <- c("barcode", "ic_correct_length")


# Mean response time and device
ic_Mean_ms <- plyr::ddply(ic, "barcode", summarise, icMean_mil_sec = mean(response_ms), device_name2 = unique(device_name2))

ic_reduced <- list(ic_iscorrect_sum,ic_Mean_ms,ic_iscorrect_length) %>%
    Reduce(function(dtf1,dtf2) full_join(dtf1,dtf2,by="barcode"), .)


# measuring proportion of correct answer
ic_reduced$ic_correct_prop <- ic_reduced$ic_correct_sum/ic_reduced$ic_correct_length
```


```{r Saving Merged file}
setwd("C:/Gene_cognition_shafiq/02_Cleaning_Cognitive_data/Aggregated_Clean_Cognitive_Data")
fwrite(ic_reduced, file = "Stroop_Ink_Aggregated_Feb2022.txt", sep = "\t", col.names = TRUE, row.names = FALSE, quote=FALSE)
```


