---
title: "Trail Making"
author: "Shafiq"
date: "08/03/2022"
output: html_document
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
library(data.table)
library(patchwork)
library(forcats)
library(knitr)
library(lubridate)
library(dplyr)
library(tidyr)
library(stringr)
library(MASS)
library(gplots)
library(RColorBrewer)
library(rmarkdown)
library(skimr)
library(ggpubr)
library(psych)
```

# Reading pilot data
```{r Reading pilot file, echo = TRUE, warning = FALSE}
setwd("C:/NIHR_Bioresource/Orginal_Data/Gene_and_cognition_study/Emma_har/G&C_Main_Phase1_Pilot_new/results_20200825_Modified_SPIDs")

ts.p <- fread("results_ts_20200825_PIDRemoved_MOD.csv") 
```

# Reading Main Data
```{r Reading data, echo = FALSE, warning = FALSE}
setwd("C:/NIHR_Bioresource/Orginal_Data/Gene_and_cognition_study/Emma_har/G&C_Main_Phase1_Cognitive_Data/G&P Main phase cognitive data - Part 3_Updated_17.06.2022")

ts.m <- fread("results_ts_20211130_PIDRemoved.csv")
```


# Removing duplicates from Trail Numeric test
```{r Trails Numeric}
ts.m_num <- ts.m %>% filter(test_name=="TrailsNumeric")

ts.m_num %>% 
  group_by(barcode) %>% 
  count() %>% 
  pull(n) %>% 
  table()

ts.m_num %>% 
  group_by(barcode) %>%
  filter(n() > 24) %>% 
  count()

ts.m_num_nodups <- ts.m_num %>% 
  mutate(time_stamp2 = dmy_hms(time_stamp)) %>% 
  arrange(barcode, question, time_stamp2) %>% 
  mutate(exactDuplicate = duplicated(.)) %>%  
  mutate(diffDateTimeDuplicate = !exactDuplicate & {dplyr::select(., barcode, question) %>% duplicated()})

dup_tests_removed <- ts.m_num_nodups %>% filter(exactDuplicate | diffDateTimeDuplicate) 

ts.m_num_nodups <- ts.m_num_nodups %>% 
  filter(!exactDuplicate & !diffDateTimeDuplicate) %>% 
  dplyr::select(colnames(ts.m_num))
```


# Removing duplicates from Trail Alpha Numeric test
```{r Alpha Numeric Test}
ts.m_alpha <- ts.m %>% filter(test_name=="TrailsAlphanumeric")

ts.m_alpha %>% 
  group_by(barcode) %>% 
  count() %>% 
  pull(n) %>% 
  table()

ts.m_alpha %>% 
  group_by(barcode) %>%
  filter(n() > 24) %>% 
  count()

ts.m_alpha_nodups <- ts.m_alpha %>% 
  mutate(time_stamp2 = dmy_hms(time_stamp)) %>%
  arrange(barcode, question, time_stamp2) %>%
  mutate(exactDuplicate = duplicated(.)) %>%
  mutate(diffDateTimeDuplicate = !exactDuplicate & {dplyr::select(., barcode, question) %>% duplicated()}) 


dup_tests_removed <- ts.m_alpha_nodups %>% 
  filter(exactDuplicate | diffDateTimeDuplicate) 

dup_tests_removed %>% 
  group_by(barcode, exactDuplicate, diffDateTimeDuplicate) %>% 
  count()

ts.m_alpha_nodups  <- ts.m_alpha_nodups  %>% 
  filter(!exactDuplicate & !diffDateTimeDuplicate) %>% 
  dplyr::select(colnames(ts.m_alpha))
```


# Merging cleaned main and pilot phase data 
```{r, echo = FALSE, warning = FALSE}
ts.m <- full_join(ts.m_num_nodups,ts.m_alpha_nodups)
```


# Device
```{r Deive use, echo = FALSE, warning = FALSE}
ts$device_name2 <- as.character(ts$device_name)
ts$device_name2[grep("Windows", ts$device_name2, ignore.case = TRUE)] <- "Windows 10"
ts$device_name2[grep("iphone", ts$device_name2, ignore.case = TRUE)] <- "iPhone"
ts$device_name2[grep("android", ts$device_name2, ignore.case = TRUE)] <- "Android"
ts$device_name2 <- as.factor(ts$device_name2)
```


# There were no value <=0 with Minimim non-zero score.
```{r}
summary(ts$response_ms)
# Mean=12593
# Median=8347
zero_below <-ts %>% filter(response_ms<=0) # 0 obs
```


# All trails tests together 
```{r Aggregates Analysis of Trail test results}
# Number of guess
ts_num_guess <- aggregate(ts$guesses, by = list(ts$barcode), FUN = sum, na.rm=TRUE)
names(ts_num_guess) <- c("barcode", "ts_total_guesses")

#is correct length
ts_guess_length <- aggregate(ts$guesses, by = list(ts$barcode), FUN = length)
colnames(ts_guess_length) <- c("barcode", "ts_guess_length")
table(ts_guess_length$ts_guess_length, useNA = "a")
sum(table(ts_guess_length$ts_guess_length, useNA = "a"))

# mean response time and device
ts_Mean_ms <- plyr::ddply(ts, "barcode", summarise, tsMean_mil_sec = mean(response_ms), device_name2 = unique(device_name2))

ts_reduced <- list(ts_num_guess,ts_Mean_ms,ts_guess_length) %>%
    Reduce(function(dtf1,dtf2) full_join(dtf1,dtf2,by="barcode"), .)



# measuring proportion of correct guess
ts_reduced$ts_incorr_guess_prop <- ts_reduced$ts_total_guesses/ts_reduced$ts_guess_length
```


# Seprating Numeric Trail test  
```{r}
ts_num <- ts %>% filter(test_name=="TrailsNumeric")
ts_num_guess_length <- aggregate(ts_num$guesses, by = list(ts_num$barcode), FUN = length)
colnames(ts_num_guess_length) <- c("barcode", "ts_num_guess_length")

# Number of guess
ts_num_guess <- aggregate(ts_num$guesses, by = list(ts_num$barcode), FUN = sum, na.rm=TRUE)
names(ts_num_guess) <- c("barcode", "ts_num_total_guesses")

tsNum_Mean_ms <- plyr::ddply(ts_num, "barcode", summarise, ts_num_Mean_mil_sec = mean(response_ms))

ts_num_reduced <- list(ts_num_guess,tsNum_Mean_ms,ts_num_guess_length) %>% Reduce(function(dtf1,dtf2) full_join(dtf1,dtf2,by="barcode"), .)

ts_num_reduced$ts_num_incorr_guess_prop <- ts_num_reduced$ts_num_total_guesses/ts_num_reduced$ts_num_guess_length
```



# Seprating Alpha Numeric Trail test  
```{r}
ts_alpha <- ts %>% filter(test_name=="TrailsAlphanumeric")
ts_alpha_guess_length <- aggregate(ts_alpha$guesses, by = list(ts_alpha$barcode), FUN = length)


# Number of guess
ts_alpha_guess <- aggregate(ts_alpha$guesses, by = list(ts_alpha$barcode), FUN = sum, na.rm=TRUE)
names(ts_alpha_guess) <- c("barcode", "ts_alpha_total_guesses")

# mean response time and device
tsAlpha_Mean_ms <- plyr::ddply(ts_alpha, "barcode", summarise, ts_alpha_Mean_mil_sec = mean(response_ms))

ts_alpha_reduced <- list(ts_alpha_guess,tsAlpha_Mean_ms,ts_alpha_guess_length) %>%
    Reduce(function(dtf1,dtf2) full_join(dtf1,dtf2,by="barcode"), .)

# measuring proportion of correct guess
ts_alpha_reduced$ts_alpha_incorr_guess_prop <- ts_alpha_reduced$ts_alpha_total_guesses/ts_alpha_reduced$ts_alpha_guess_length
```


# Combine summary data for both tests and plot
```{r}

ts_aggregated <- list(ts_reduced, ts_num_reduced, ts_alpha_reduced) %>%
    Reduce(function(dtf1,dtf2) full_join(dtf1,dtf2,by="barcode"), .)

ts_rsp_times <- log10(ts_aggregated[,c(3,8,12)])

setwd("C:/Gene_cognition_shafiq/02_Cleaning_Cognitive_data/Aggregated_Clean_Cognitive_Data")
fwrite(ts_aggregated, file = "Trails_Aggregated_Feb2022.txt", sep = "\t", col.names = TRUE, row.names = FALSE, quote=FALSE)
```








